A new tidy data structure to support exploration and modeling of temporal data

### 2019-01-18 main.Rmd
section 3.0 done

The choice of tidy representation of temporal data arises from a data-centric perspective, which accommodates all of the operations that are to be performed on the data. Figure \@ref(fig:tsibble-fit) marks where this new abstraction is placed in the tidy model, which we refer to as "tsibble".

@@

Table \@ref(tab:tb-sub) presents a subset of tuberculosis cases estimated by @tb-data. It contains 12 observations and 5 variables arranged in a "long" tabular form. Each observation hosts the number of people who are diagnosed tuberculosis for each gender at three selected countries in the years of 2011 and 2012. To turn this data into a tsibble, (1) column `year` is declared as the index variable; (2) the key can be made up of columns `country` and `gender`. Despite column `count` is the only measurement in this case, it is sufficiently flexible to hold other measured variables, for example, adding the corresponding population size (if known) in order to calibrate the count later.

It bridges the gap between raw temporal data and model inputs. Contextual semantics are introduced to tidy data in order to support more intuitive time-related manipulations and enlighten new perspectives for time series model inputs. Index, key and time interval are the three stone pillars to this new semantically-structured temporal data.

>>>>

The choice of tidy representation of temporal data arises from a data-centric perspective, which accommodates all of the operations that are to be performed on the data. Figure \@ref(fig:tsibble-fit) marks where this new abstraction is placed in the tidy model, which we refer to as a "tsibble".

@@

Table \@ref(tab:tb-sub) presents a subset of tuberculosis cases estimated by @tb-data. It contains 12 observations and 5 variables arranged in a "long" tabular form. Each observation hosts the number of people who are diagnosed tuberculosis for each gender at three selected countries in the years of 2011 and 2012. To turn this data into a tsibble, (1) column `year` is declared as the index variable; (2) the key can be made up of columns `country` and `gender`. The column `count` is the only measured variable in this data, but the structure is sufficiently flexible to hold other measured variables, for example, adding the corresponding population size (if known) in order to calibrate the count later.

The new data structure, tsibble, bridges the gap between raw temporal data and model inputs. Contextual semantics are introduced to tidy data in order to support more intuitive time-related manipulations and enlighten new perspectives for time series model inputs. Index, key and time interval are the three stone pillars to this new semantically-structured temporal data.
